Measuring the dust opacity of the debris disk around HD 107146 with transit photometry

### 2023-09-29 src/tex/ms.tex
[showyourwork] overleaf sync

\begin{figure*}[ht]
    \centering
    \includegraphics[width=17cm]{figures/GS01.eps}
    \caption{Top four rows (incremental differential field orientations): Visit-level reductions after step 5 (PSF template subtraction) in Science Instrument Aperture Frame with rotationally invariant PSF and disk/galaxy co-rotating with telescope orientation. Bottom row: Epoch-level reductions after step 8 (multi-roll combination in “north up” (NUP) orientation).  Central regions digitally masked as black are unsampled or degraded due to STIS occulting masks, HST diffraction spikes or other image/PSF-subtraction artifacts. Left to right columns: epoch 0 to epoch 7.}
    \label{fig:GS01}
\end{figure*}

\begin{figure*}[ht]
    \centering
    \includegraphics[width=17cm]{figures/GS02.eps}
    \caption{HD107146 debris ring transit (ingress) over background galaxy - chronologically  in panels E0 - E7. Same as \autoref{fig:GS01} bottom row (NUP) images, but illustrated in more detail.  Panels E0/E1 epochs with galaxy located at “pre-transit” periphery of debris ring re-reduced from GO 12228. Other panels (starting ~ 6 years later) are twice a year with unequal cadence per HST scheduling constraints (assuring coronagraphically obscured regions do not superimpose on the location of the galaxy with other spacecraft orientations constraints). All images are astrometrically co-registered on the obscured central star (position indicated by small red dot), are shown as log10 stretch from [-2] to [-0.7] dex counts/sec/per pixel; north up, 300x300 pixel sub-array extracts centered on target. (1 pixel = $50.077$ mas). FOVs extend further west than illustrated and provide a basis for background noise estimation.  The vermin galaxy has a peak surface brightness (Gmax) of $\sim 0.5$ counts/sec/per pixel, the disk at the same stellocentric angular distance with Dmax $\sim 0.04$ counts/sec/pixel, and a background (at large distance from the star and galaxy with RMS noise $\sigma_{rms} \approx 3\times 10^{-3}$.}
    \label{fig:GS02}
\end{figure*}

@@

\begin{figure*}[ht]
    \centering
    \includegraphics[width=17cm]{figures/GS03.jpg}
    \caption{Left: Epoch 0+1 AQ image of the HD 107146 debris ring fully sampled with the Vermin galaxy well separated beyond the periphery of the disk. Linear display range $\pm 0.05$ counts per second per pixel to show the structure of remaining PSF-subtraction residuals without saturating at the radius of highest surface brightness while also revealing the low level of “pixel to pixel” noise in the sky background at the field boundaries.  Middle: Model disk image at same display stretch derived from all eight epochs with galaxy masked. Right: Representative surface brightness radial profile/cross-section (arbitrarily along disk major axis) comparison of AQ image (solid line) vs. model comparison (dot-dashed line) showing excellent agreement at $r > 65$ pixels ($3.3”$) in region of interest of galaxy reflex motion at epochs 0 – 7 inclusive.}
    \label{fig:GS03}
\end{figure*}

\begin{figure*}[ht]
    \centering
    \includegraphics[width=17cm]{figures/GS04.eps}
    \caption{Illustration of of disk-light rejection by model subtraction. Left: Representative (epoch 2) AQ image. Right: model disk (same as in \autoref{fig:GS03}). Right: Galaxy image with disk-light rejection. Unmodeled high spatial frequency stellocentric radial PSF-subtraction artifacts persist, but are well separated from the galaxy and non-impacting in all epoch 0 – 7 images.}
    \label{fig:GS04}
\end{figure*}

>>>>

% \begin{figure*}[ht]
%     \centering
%     \includegraphics[width=17cm]{figures/GS01.eps}
%     \caption{Top four rows (incremental differential field orientations): Visit-level reductions after step 5 (PSF template subtraction) in Science Instrument Aperture Frame with rotationally invariant PSF and disk/galaxy co-rotating with telescope orientation. Bottom row: Epoch-level reductions after step 8 (multi-roll combination in “north up” (NUP) orientation).  Central regions digitally masked as black are unsampled or degraded due to STIS occulting masks, HST diffraction spikes or other image/PSF-subtraction artifacts. Left to right columns: epoch 0 to epoch 7.}
%     \label{fig:GS01}
% \end{figure*}

% \begin{figure*}[ht]
%     \centering
%     \includegraphics[width=17cm]{figures/GS02.eps}
%     \caption{HD107146 debris ring transit (ingress) over background galaxy - chronologically  in panels E0 - E7. Same as \autoref{fig:GS01} bottom row (NUP) images, but illustrated in more detail.  Panels E0/E1 epochs with galaxy located at “pre-transit” periphery of debris ring re-reduced from GO 12228. Other panels (starting ~ 6 years later) are twice a year with unequal cadence per HST scheduling constraints (assuring coronagraphically obscured regions do not superimpose on the location of the galaxy with other spacecraft orientations constraints). All images are astrometrically co-registered on the obscured central star (position indicated by small red dot), are shown as log10 stretch from [-2] to [-0.7] dex counts/sec/per pixel; north up, 300x300 pixel sub-array extracts centered on target. (1 pixel = $50.077$ mas). FOVs extend further west than illustrated and provide a basis for background noise estimation.  The vermin galaxy has a peak surface brightness (Gmax) of $\sim 0.5$ counts/sec/per pixel, the disk at the same stellocentric angular distance with Dmax $\sim 0.04$ counts/sec/pixel, and a background (at large distance from the star and galaxy with RMS noise $\sigma_{rms} \approx 3\times 10^{-3}$.}
%     \label{fig:GS02}
% \end{figure*}

@@

% \begin{figure*}[ht]
%     \centering
%     \includegraphics[width=17cm]{figures/GS03.jpg}
%     \caption{Left: Epoch 0+1 AQ image of the HD 107146 debris ring fully sampled with the Vermin galaxy well separated beyond the periphery of the disk. Linear display range $\pm 0.05$ counts per second per pixel to show the structure of remaining PSF-subtraction residuals without saturating at the radius of highest surface brightness while also revealing the low level of “pixel to pixel” noise in the sky background at the field boundaries.  Middle: Model disk image at same display stretch derived from all eight epochs with galaxy masked. Right: Representative surface brightness radial profile/cross-section (arbitrarily along disk major axis) comparison of AQ image (solid line) vs. model comparison (dot-dashed line) showing excellent agreement at $r > 65$ pixels ($3.3”$) in region of interest of galaxy reflex motion at epochs 0 – 7 inclusive.}
%     \label{fig:GS03}
% \end{figure*}

% \begin{figure*}[ht]
%     \centering
%     \includegraphics[width=17cm]{figures/GS04.eps}
%     \caption{Illustration of of disk-light rejection by model subtraction. Left: Representative (epoch 2) AQ image. Right: model disk (same as in \autoref{fig:GS03}). Right: Galaxy image with disk-light rejection. Unmodeled high spatial frequency stellocentric radial PSF-subtraction artifacts persist, but are well separated from the galaxy and non-impacting in all epoch 0 – 7 images.}
%     \label{fig:GS04}
% \end{figure*}
